Particle Interception as a Function of Reynolds Number and Collector Density

### 2020-10-17 code/analysis.Rmd
rly rly fixed ece plot

plotece2 <- final %>%
  filter(dowel_density != "0000") %>%
  mutate(Refac = factor(Re, labels = c("Re = 66.78", "Re = 133.56", "Re = 200.34"))) %>%
  ggplot(aes(lty = factor(round(Re, 0)), y = eta, ymin = eta - deta, ymax = eta + deta, x = factor(ad, labels = c("0.22%","0.64%","1.17%")))) +
  geom_point(position = position_dodge(width = .55)) +
  geom_errorbar(width = 0.4, position = position_dodge(width = .55)) +  
  scale_y_continuous(labels = scales::percent) +
  labs(y = "ECE", lty = expression(Re[c]), x = expression(phi[c])) +
  theme_bw() +
  theme(legend.position = "bottom")

>>>>

plotece2 <- final %>%
  filter(dowel_density != "0000") %>%
  mutate(Refac = factor(Re, labels = c("Re = 66.78", "Re = 133.56", "Re = 200.34"))) %>%
  ggplot(aes(color = factor(round(Re, 0)), y = eta, ymin = eta - deta, ymax = eta + deta, x = factor(ad, labels = c("0.22%","0.64%","1.17%")))) +
  geom_point(position = position_dodge(width = .55)) +
  geom_errorbar(width = 0.4, position = position_dodge(width = .55)) +  
  scale_y_continuous(labels = scales::percent) +
  scale_color_manual(values = c("purple","orange","brown")) +
  labs(y = "ECE", color = expression(Re[c]), x = expression(phi[c])) +
  theme_bw() +
  theme(legend.position = "bottom")
